---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countallmissing

<!-- badges: start -->
<!-- badges: end -->

The goal of countallmissing is to count missing values for all columns by group in a data set. 

This function is a wrapper around the `group_by()` and `summarize()` functions in the `dplyr` package.

Given a data frame `data` and a column `group`, **count_all_missing_by_group()** creates a new data frame with one row per level of `group`. The first column of the output data frame contains the levels of `group`, and the rest of the columns contain the number of missing values for all columns in `data` except `group`.

## Installation

You can install the development version of countallmissing like so:

``` r
devtools::install_github("https://github.com/stat545ubc-2023/assignment-b2-hhauch.git", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(countallmissing)
count_all_missing_by_group(airquality, Month)
```

